Advantages of mixed unitary operators for quantum information processing

### 2018-12-08 decorrelation/mixed_unitaries.tex
small changes in the text, biggest is changing supremacy -> advantage

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIP). Gate fidelities are now routinely in the 99\% to 99.99\% range, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum supremacy milestone has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

The impact of an error in a quantum gate depends strongly on both the nature of the errors. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations. These errors induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time and add up coherently, so they are computationally expensive to model and it is difficult to place analytic bounds on circuit performance. Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment. These errors can be modeled by defining a rate of various discrete errors in the system, such as a bit flip or phase flip. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.

@@

% ==============================================================================
% Section: Example Mixed Unitary Processes
% ==============================================================================
\section{Example Mixed Unitary Processes}
\label{sec:mixed_unitary_processes}
There are often many possibly ways of implementing a target quantum gate. Hastings and Campbell consider gates compiled using the Solovey-Kitaev algorithm, for which there are many choices of approximate quantum gate implementations. By implementing some number o these implementations at random, we are able to construct a quantum channel that has reduced coherent error. As a simple example, we have:

>>>>

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

The impact of an error in a quantum gate depends strongly on both the magnitude and nature of the errors. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations. These errors induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time and add up coherently, so they are computationally expensive to model and it is difficult to place analytic bounds on circuit performance. Contrast this against random, or \emph{stochastic}, errors, which result from high-frequency noise in the controls or the environment. These errors can be modeled by defining a rate of various discrete errors in the system, such as a bit flip or phase flip. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate.

@@

% ==============================================================================
% Section: Example Mixed Unitary Processes
% ==============================================================================
\section{Example Mixed Unitary Processes}
\label{sec:mixed_unitary_processes}
There are often many possibly ways of implementing a target quantum gate. Hastings and Campbell consider gates compiled using the Solovey-Kitaev algorithm, for which there are many choices of approximate quantum gate implementations. By implementing some number of these implementations at random, we are able to construct a quantum channel that has reduced coherent error. As a simple example, we have:
